Precise spiking motifs in neurobiological and neuromorphic data

### 2022-11-08 manuscript.tex
Update on Overleaf.

Translated with www.DeepL.com/Translator (free version)

@@

Mt#the limits that we have
presented can be treated individually
as evidenced by individual efforts
which try he orecome them. However,
to propose a real breakthrough, we
believe that future venues should
provide with a unified, inter-disciplinary
approach, with applications to deal-
word, ecological scenarios and
with open and reproducible methods.
First, as we already noted, the effort
is still largely scattered -this is
in part due to the fact that interaction
between neurobiology, theoretical
and computational neuroscience
and meromorphic engineering
are still scarce as of today.
It was largely demonstrated that
close, bi-directional interactions
are essential to foster breakthrough
For instance, the design of model-
driven protocols as proven to be
essential in modern neuroscience.
Also, if neural networks were
essential in shaping modern-day
machine learning, e-g. computer
vision using deep-learning,
spiking neural networks should
prove essential in future
emerging technologies.

>>>>

@@

The limits that we have
presented can be treated individually
as evidenced by individual efforts
which try he orecome them. However,
to propose a real breakthrough, we
believe that future venues should
provide with a unified, inter-disciplinary
approach, with applications to deal-
word, ecological scenarios and
with open and reproducible methods.
First, as we already noted, the effort
is still largely scattered -this is
in part due to the fact that interaction
between neurobiology, theoretical
and computational neuroscience
and meromorphic engineering
are still scarce as of today.
It was largely demonstrated that
close, bi-directional interactions
are essential to foster breakthrough
For instance, the design of model-
driven protocols as proven to be
essential in modern neuroscience.
Also, if neural networks were
essential in shaping modern-day
machine learning, e-g. computer
vision using deep-learning,
spiking neural networks should
prove essential in future
emerging technologies.
